Type Refinements for the Working Class

### 2015-11-27 paper.tex
Introduce PER abbreviation

\begin{definition}
  To know $\Refines{\Upsilon}{\phi}{\tau}$ (presupposing $\IsSymCtx{\Upsilon}$
  and $\IsSort{\tau}$) is to know, for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd},
  what it means for any $\Member{M,N}{\Exprs_\tau(\Upsilon')}$ to be equated by
  $\phi$ (written $\RefEquate{\phi}{\rho}{M}{N}$), such that
  $\RefEquate{\phi}{\rho}{-}{-}$ is a partial equivalence relation on
  $\Exprs_\tau(\Upsilon')$. Morever, that for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r,hook,"\IMode{\rho'}"] &\IMode{\Upsilon''}
  \end{tikzcd},
  from $\RefEquate{\phi}{\rho}{M}{N}$ we may conclude
  $\RefEquate{\phi}{\rho'\circ\rho}{M\rho'}{N\rho'}$.
\end{definition}

>>>>

\begin{definition}
  To know $\Refines{\Upsilon}{\phi}{\tau}$ (presupposing $\IsSymCtx{\Upsilon}$
  and $\IsSort{\tau}$) is to know, for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd},
  what it means for any $\Member{M,N}{\Exprs_\tau(\Upsilon')}$ to be equated by
  $\phi$ (written $\RefEquate{\phi}{\rho}{M}{N}$), such that
  $\RefEquate{\phi}{\rho}{-}{-}$ is a partial equivalence relation (PER) on
  $\Exprs_\tau(\Upsilon')$. Morever, that for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r,hook,"\IMode{\rho'}"] &\IMode{\Upsilon''}
  \end{tikzcd},
  from $\RefEquate{\phi}{\rho}{M}{N}$ we may conclude
  $\RefEquate{\phi}{\rho'\circ\rho}{M\rho'}{N\rho'}$.
\end{definition}
